---
title: "Linear Models"
author: "Emma Sexton"
date: "2022-11-14"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
```


Load NYC Airbnb Data

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group
  ) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighbourhood, room_type)
```


## Fit the first model

```{r}
fit = lm(price ~ stars + borough, data = nyc_airbnb)

fit
# tells you coefficients
```


Can start extracting (gives you more info)
```{r}
summary(fit)

summary(fit)$coef
```


```{r}
fit %>% 
  broom::tidy() %>% 
  mutate(
    term = str_replace(term, "borough", "Borough: ")
  ) %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 2)
```

How would you change the reference category to a different borough?

* what's happening in the background is R is just putting it in alphabetical order
* if that's not what you want to do, you can do the following:
  * `fct_infreq` = the most common category

```{r}
fit = 
  nyc_airbnb %>% 
  mutate(
    borough = fct_infreq(borough)
  ) %>% 
  lm(price ~ stars + borough, data = .)

fit %>% 
  broom::tidy() %>% 
  mutate(
    term = str_replace(term, "borough", "Borough: ")
  ) %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 2)
```

Can also include the `borough = fct_infreq` in the data cleaning (if that's what you want to do throughout all analyses and visualizations)

```{r}
fit %>% 
  broom::glance() %>% 
  select(AIC)
# gives you r^2, signma, etc. -- lots of stuff
```



## Diagnostics 

Putting residuals in the data frame

```{r}
modelr::add_residuals(nyc_airbnb, fit) %>%
  ggplot(aes(x = stars, y = resid)) +
  geom_point()
```

They're suppposed to be mean 0 and constant variance -- at the very least, we're running into issues there (lots more variance in 4-5 compared to 1-3)

* Constant variance assumption doesn't work here
* Doesn't mean our regression is invalid
* If we wanted to do hypothesis testing, we might have to be concerned about non-constant variance
* If you wanted to get a confidence interval for the effect of stars, maybe you do have to worry about this
* If you wanted to exclude outliers -- maybe that'd make sense

```{r}
nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = borough, y = resid)) +
  geom_violin() +
  ylim(-250, 250)
```

Here, assumptions aren't met but the sample size is big -- don't know what to do here.

## Hypothesis testing

One coefficient (let's say `stars`).

```{r}
fit %>% 
  broom::tidy()

fit_null = lm(price ~ stars, data = nyc_airbnb)
fit_alt = lm(price ~ stars + borough, data = nyc_airbnb)

anova(fit_null, fit_alt) %>% 
  broom::tidy()
```






